### 2014-04-30 examples/qval.nonp.rmd
update README for Rcpp and non-Rcpp versions

Now we perform a "sanity check" for each method, comparing its $q$-values against the
nonparametric $q$ values obtained using the same estimate of $\pi_0$. Both `ash` and `qvalue`
clearly pass this sanity check (for `qvalue`, this is almost tautological, since it effectively uses the non-parametric procedure). For `locfdr`, it also passes the sanity check except for
some artifacts near $p=1$ that we do not fully understand. For `mixfdr` there seems to be a systematic deviation from the non-parametric method that suggests.
```{r}
  par(mfcol=c(2,2))
  plot(qval.nonp(p,get_pi0(test.ash)),test.ash$qvalue, xlab="nonparametric q-values (with pi0 estimated by ash)", ylab = "ash q-values",main="ash")
  abline(a=0,b=1,col=2,lwd=2)

@@

Although these simulations are by no-means comprehensive, they show that, for these the primary
difference

>>>>

Now we perform a "sanity check" for each method, comparing its $q$-values against the
nonparametric $q$ values obtained using the same estimate of $\pi_0$. Both `ash` and `qvalue`
clearly pass this sanity check (for `qvalue`, this is almost tautological, since it effectively uses the non-parametric procedure). For `locfdr`, it also passes the sanity check except for
some artifacts near $p=1$ that we do not fully understand. For `mixfdr` there seems to be a systematic deviation from the non-parametric method that suggests...
```{r}
  par(mfcol=c(2,2))
  plot(qval.nonp(p,get_pi0(test.ash)),test.ash$qvalue, xlab="nonparametric q-values (with pi0 estimated by ash)", ylab = "ash q-values",main="ash")
  abline(a=0,b=1,col=2,lwd=2)

@@

Although these simulations are by no-means comprehensive, they show that, for these the primary
difference between ash $q$ values and qvalue $q$ values is
the different estimates of $\pi_0$.
